14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Fix

\header{Competition Website.}
The competition website (\url{www.smtcomp.org}) will be used as the main form
of communication for the competition. The website will be used to post updates,
link to these rules and other relevant information (e.g. the benchmarks), and
to announce the results. We also use the website to archive previous
competitions. Starting from 2019 we will include the submitted solvers in this
archive to allow reproduction of the competition results in the future.
%

\header{Tools.}
The competition uses a number of tools/scripts to run the competition. In the
following, we briefly describe these tools. Unless stated otherwise, these
tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
{\color{red} Some tools have not been released yet.}
\begin{itemize}
  \item \textbf{Benchmark Selection.} We use a script to implement the
    benchmark selection policy described on page~\pageref{benchmark-selection}.
    It takes a seed for the random benchmark selection. The same seed is used
    for all tools requiring randomisation.
  \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
    competition to ensure that tools do not rely on syntactic features to
    identify benchmarks. The scrambler can be found at
    \url{https://github.com/SMT-COMP/scrambler}.
  \item \textbf{Trace Executor.} This tool is used in the \inctrack to emulate
    an on-line interaction between an SMT solver and a client application and
    is available at \url{https://github.com/SMT-COMP/trace-executor}
  \item \textbf{Postprocessors.} These are used by StarExec to translate the
    output of tools to the format required for scoring. All postprocessors (per
    track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
  \item \textbf{Scoring.} We use a script to implement the scoring computation
    described on in Section~\ref{sec:scoring}. It also includes the scoring
    computations used in previous competitions (since 2015).
\end{itemize}

>>>>

\header{Competition Website.}
%
The competition website (\url{www.smtcomp.org}) will be used as the main form
of communication for the competition. The website will be used to post updates,
link to these rules and other relevant information (e.g. the benchmarks), and
to announce the results. We also use the website to archive previous
competitions. Starting from 2019 we will include the submitted solvers in this
archive to allow reproduction of the competition results in the future.

\header{Tools.}
%
The competition uses a number of tools/scripts to run the competition. In the
following, we briefly describe these tools. Unless stated otherwise, these
tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
{\color{red} Some tools have not been released yet.}
\begin{itemize}
  \item \textbf{Benchmark Selection.} We use a script to implement the
    benchmark selection policy described on page~\pageref{benchmark-selection}.
    It takes a seed for the random benchmark selection. The same seed is used
    for all tools requiring randomisation.
  \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
    competition to ensure that tools do not rely on syntactic features to
    identify benchmarks. The scrambler can be found at
    \url{https://github.com/SMT-COMP/scrambler}.
  \item \textbf{Trace Executor.} This tool is used in the \inctrack to emulate
    an on-line interaction between an SMT solver and a client application and
    is available at \url{https://github.com/SMT-COMP/trace-executor}
  \item \textbf{Postprocessors.} These are used by StarExec to translate the
    output of tools to the format required for scoring. All postprocessors (per
    track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
  \item \textbf{Scoring.} We use a script to implement the scoring computation
    described in Section~\ref{sec:scoring}. It also includes the scoring
    computations used in previous competitions (since 2015).
\end{itemize}
